---
title: "A glimps of the package morphRiver"
author: "L.Vaudor"
date: "4 decembre 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

Let us consider points (loaded from a shapefile) and a DEM (loaded from a .tif file)

```{r}
points=st_read(system.file("data/points.shp", package="morphRiver"))
rasterDEM=raster(system.file("data/rasterDEM.tif", package="morphRiver"))
```

Here is a view of the data in these files

```{r, fig.height=8}
plot(rasterDEM)
plot(points,
     add=TRUE, col=1)
```

We'll now use the package `morphRiver`:

```{r}
library(morphRiver)
```


# Curvature

## Calculate curvature

Only the set of points is needed to calculate curvature:

```{r}
rcurv=curvature(points) %>% points_to_linestring()
print(rcurv)
```

## Show result

### on map

```{r, fig.height=8}
plot(rasterDEM)
plot(points,
     add=TRUE, col=1)
plot(rcurv["C"],
    add=TRUE, lwd=3)
```

### as longitudinal signal

```{r, fig.height=4, fig.width=8}
library(ggplot2)
ggplot(data=rcurv, aes(x=S,y=C))+
  geom_path()
```

# Calculate basin width

## Calculate elevation

To calculate the elevation we need the set of points as well as the raster DEM

```{r}
relev=elevation(points,rasterDEM) %>% points_to_linestring()
print(relev)
```

## Transects

Calculating the basin width requires calculating the series transects going through our points:

```{r, fig.height=8}
plot(rasterDEM)
plot(points,
      add=TRUE, col=1)
plot(points_to_linestring(points),
    add=TRUE, col=2)
plot(transects(points,500),
     add=TRUE, col=4)
```

## Basin width

To calculate the basin width we'll need to provide both the points and the DEM raster (the function `transects()` is used internally):

```{r}
rwidth=basin_width(points,rasterDEM, radius=500)
print(rwidth)
```


## Show result



### on map

```{r, fig.height=8}
plot(rasterDEM)
plot(rwidth,
    add=TRUE, col=4, lwd=3)
```

### as longitudinal signal

```{r}
library(ggplot2)
ggplot(data=rwidth, aes(x=S,y=W))+
 geom_path()
```

